---
title: "Generalized Reg - Worksheet 3"
author: "Tiziana Errera"
date: "05/10/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1 



A study looking at breast cancer in women compared cases with non-cases, and found that
75/100 cases did not use calcium supplements compared with 25/100 of the non-cases.

#a - Develop a 2 x 2 table to display the data.

```{r data}
xt <- matrix(c("a", "b", "c", "d"),ncol=2,byrow=TRUE)
colnames(xt) <- c("Diseased","Healthy")
rownames(xt) <- c("Exposed", "Not Exposed")
xt <- as.table(xt)
xt
x <- matrix(c(25,75, 75,25),ncol=2,byrow=TRUE)
 colnames(x) <- c("Case - Diseased","Control - Healthy")
 rownames(x) <- c("Exposed", "Not Exposed")
 x <- as.table(x)
 x


```

#b - Calculate the odds ratio (OR) based on the 2 x 2 table.

 
The Odds Ratio: (axd)/(bxc) = (25x25)/(75x75) = 0.11


#c - Interpret the odds ratio.

This odds indicate clearly that the exposition of calcium supplement has protective effect, the reduced risk is 89% (1-0.1*100) for exposure.
 

#d - Define the following data frame in R and fit the binary logistic regression model by using the below glm() function.

```{r data_frame and model}

disease <- factor(c(rep(1, 75), rep(0, 25), rep(1, 25), rep(0, 75)),
levels = c("1", "0"),
labels = c("yes", "no"))
supp <- factor(c(rep("no.calc", 100), rep("calc", 100)),
levels = c("no.calc", "calc"),
labels = c("no.calc", "calc"))
RCT <- data.frame(disease = disease,
supp = supp)
table(RCT$supp, RCT$disease)
bin.log.mod <- glm(disease ~ supp, family = "binomial", data = RCT)

```

#e - How can you extract the (same) odds ratio as calculated in b) from the glm() model?

```{r oddsratio}

odds_ratio <- exp(coef(bin.log.mod))^-1

output<- c("The odds ratio is: ", round(odds_ratio[2], digits = 2))
output


```
##Exercise 2

The CHFLS data set from package HSAUR2 is a subset of the Chinese Health and Family Life
Survey (cf. Exercise 3, Worksheet 1).
We want to study the impact of age and income on happiness in a proportional odds logistic
model. For this, the following polr() model is fitted:

```{r upload}

library("MASS")
data("CHFLS", package = "HSAUR2")
polr.mod <- polr(R_happy ~ R_age + R_income, data = CHFLS)

```

Happy it has been defined in a ordered logistic regression model, 
#a - What are the characteristics of the response variable R_happy? 
Apply the following commands to the previously defined R object polr.mod.

```{r summary}

summary(polr.mod)
c(polr.mod$zeta, coef(polr.mod))
exp(c(polr.mod$zeta, coef(polr.mod)))

```